Group invariance 

### 2020-12-21 docs/paper.Rmd
update sección invarianza

---
title: "Measuring Perceptions and Preferences for Meritocracy"
css: "custom.css"
linestretch: '1.5'
link-citations: yes
author: "Juan Carlos Castillo, Julio Iturra & Francisco Meneses <br><br>"
abstract: "Economic and social inequalities have generated growing concern and crises across contemporary societies. One of the mechanisms proposed by the social sciences to explain the maintenance of inequality is the belief in meritocracy, which would legitimize economic disparities based on differences in effort and talent. Despite its wide use as a concept, empirical research on meritocracy is relatively novel, and as it is based upon multiple approaches and techniques, its interpretation can be difficult and confusing. Adding to these difficulties, is the fact that many such studies have relied upon secondary data to operationalize meritocracy, with significant variation in the use and interpretation of survey items. Based on a review of studies that measure meritocracy, this article identifies a series of drawbacks and inconsistencies within and between studies regarding the conceptualization and indicators of meritocracy. Based on this critical analysis, we propose a scale named the *Perceptions and Preferences for Meritocracy Scale*, which we test with confirmatory factor analysis, using data from an online survey study (N=2,141). Our results support the proposed conceptual structure, which not only distinguishes between perceptions and preferences, but also between meritocratic and non-meritocratic dimensions. Our discussion highlights the importance of considering these different dimensions in order to advance the study of meritocracy."
output:
  bookdown::pdf_document2:
    template: null
    toc: false
  bookdown::html_document2:
    number_sections: false
linkcolor: blue
bibliography:
  - ../input/bib/EconomiaMoral.bib
  - ../input/bib/meritocracy.bib
editor_options:
  chunk_output_type: console
geometry: margin=0.78in
header-includes:
  # - \usepackage[spanish,es-tabla,es-nodecimaldot]{babel}
  - \usepackage{times}           # Times New Roman
  - \usepackage{caption}
  - \captionsetup[figure, table]{labelfont={bf},labelformat={default},labelsep=period}
  - \usepackage{graphicx}
  - \usepackage{float}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
---

@@

## The black-box of meritocratic beliefs {-#blackbox}

Several approaches to the empirical study of meritocracy based on public opinion surveys, refer to the concept of _beliefs_, however different meanings and operationalizations usually underlie this concept. To illustrate this point, we will take as a main reference a recent paper about meritocracy by @mijs_paradox_2019, which makes several assumptions relating to the measurement of meritocracy that are also found in previous studies. The definition of meritocratic beliefs stated by Mijs is the following: "when I discuss meritocracy beliefs, I am referring to citizens’ belief in the importance of hard work relative to structural factors." [@mijs_paradox_2019, pg.9]. In the subsequent operationalization, this is associated with the following question and indicator: "how important you think it is for getting ahead in life: (a) hard work", scored from 1 to 5 on a likert scale. There assumptions behind this definition are worth discussing in light of the conceptual meaning of meritocracy and its possibilities of operationalization.

a. _Unidimensionality_; Is merit only effort?

The item used by @mijs_paradox_2019 is part of an items' battery present in several international surveys, usually called "reasons to get ahead". This battery displays a series of indicators related to what people consider important to get ahead in life: hard work, education, ambition, a wealthy family, the right connections, religion, race, and gender. Therefore for Mijs, other aspects that could be associated with talent, such as education, are not meritocratic. As he points out: "Hard work is arguably the most meritocratic part of Michael Young’s equation: ‘Merit = Intelligence + Effort’, for the simple fact that intelligence itself is influenced by a non-meritocratic factor: who your parents happen to be" (p.5).

@@

_b. Beliefs_

The most commonly used survey items for the operationalization of meritocracy is the "reasons to get ahead" battery, which asks "how important you think it is" and then lists several factors, such as effort, education, parental wealth, and contacts. Another version of this same battery used in several surveys - sometimes along the previous one - asks about "how important you think it _should_ be".  Therefore, the question raised here is: Which one of both is a "belief"?  What _is_ or what _should_ be?

The term belief has an ambiguous character in the literature, conceived as "idea-elements" by @converseNatureBeliefSystems1964 or "considerations" by @zallerNatureOriginsMass1992. As @kluegelBeliefsInequalityAmericans2017 pointed out about the scope of beliefs: "This usage encompasses such more specific social-psychological concepts as values, perceptions, and attitudes" (p.30). Therefore, beliefs cover almost anything related to subjective factors.  To this regard, a relevant distinction in the field of inequality beliefs was made by @janmaatSubjectiveInequalityReview2013: "Perceptions refer to subjective estimates of existing inequality (i.e. thoughts about what is). Beliefs are here defined as normative ideas about just inequality (i.e. thoughts about what should be)"(p.359). Several papers dealing with meritocracy use the term beliefs (i.e. what should be), while actually referring to perceptions (i.e. what is). This occurs not only in mijs_paradox_2019, but also in @reynolds_perceptions_2014, in which the term beliefs is used to talk about perceptions, whereas other authors use general terms such as attitudes (@kunovich_systems_2007). The first attempt to shed light on this issue was made by @duru-bellat_whos_2012, who used the question "how important should the number of years spent in education and training be in deciding how much money people ought to earn?" as a proxy for "desired" meritocracy (beliefs). They then determined "perceived" meritocracy, using the questions: “Would you say that in your country, people are rewarded for their efforts?” and “... people are rewarded for their skills?”.

@@

_c. Non-meritocratic aspects_

Unlike studies that consider talent to be a non-meritocratic aspect, and therefore rule it out of the operationalization of meritocracy, @kunovich_systems_2007 follow a different approach, by including some non-meritocratic elements. Using an items’ battery listing a number of factors in relation to “How important each should be in deciding pay...” (as @duru-bellat_whos_2012 for desired meritocracy), they consider factors such as education and responsibility as meritocratic, giving them a value of 1 if considered “essential” in the scale response, whereas factors such as having a family or children are valued 1 when rated as "not important at all" (i.e. reverse coded). The assumption behind this approach is that rejecting a supposed non-meritocratic aspect (as having family and/or children) implies a larger belief in meritocracy. A similar approach of reverse-coding non-meritocratic items was taken by @newman_false_2015, using the same principles applied in the "Preference for the Merit Principle Scale" [@davey_preference_1999].

@@

_d. Accounting for measurement error_

@@

## An instrument proposal {-#instrumentprop}

@@

- _Multidimensionality_, incorporating previous distinctions between preferences and perceptions, as well as between meritocratic and non-meritocratic aspects.

- Multiple indicators for each dimension, in order to _account for measurement error_ in a confirmatory factor analysis context.

- Based on _previous indicators_ as much as possible, for the sake of comparability between studies.

- _Brief_, as to be used in regular public opinion surveys. In this respect, it differs from the proposal of  "Preference for the Merit Principle Scale" [@davey_preference_1999], as they use 15 items for just one dimension (aside from the problem of reverse-coding non-meritocratic items).

@@

* $H_1$. The perception of meritocracy is a latent variable based on indicators of the importance attributed to talent and effort to get ahead in life.

* $H_2$. The perception of non-meritocracy is a latent variable that derives from two indicators related to agreement with the statement that people with contacts and rich parents manage to get ahead.

* $H_3$. Meritocratic preferences are a latent variable based on the normative value of effort and talent.

* $H_4$. Non-meritocratic preferences are a latent variable based on the normative value of the use of personal contacts and having wealthy parents.

@@

## Data collection {-#data}

@@

With the objective of evaluating the effect of indicator ordering, the respondents (_n = 2141_) were randomly divided into three different set-order versions, as explained in Figure \@ref(fig:appmod). The scale was presented to the first group (_n = 712_) in the order that appears in Table 2. For the second group (_n = 717_), the order of the items was reorganized according to the topics of the items, e.g. for the topic of hard work, the item about perception was followed by the item about preference, and the same for the rest of the topics. Finally, for the third group (_n = 712_), the items were completely randomized.

@@

CFA was conducted using the `lavaan` R package (version 0.6-3; Rosseel, 2020), with diagonally weighted least squares (DWLS) estimation due to the items’ ordinal level of measurement (Kline, 2016; Rosseel, 2020). As recommended by Brown (2008), we assessed model fit by jointly considering the comparative fit index and Tucker-Lewis Index (CFI and TLI; acceptable fit > 0.95), Root of the average squared residual approximation (RMSEA; acceptable fit < 0.08),  Chi-square: (p-value; acceptable fit > 0.05, and Chi-square ratio > 3).

A pre-registration was made in the OSF platform, available at the following link: [https://osf.io/z45y2](https://osf.io/z45y2). Included in this pre-registration are the hypotheses regarding the four-dimensional conceptual model underlying the scale, the variable measurement levels, the statistical tests to be performed with their respective evaluation parameters, and other important aspects of the research design.

@@

As can be seen in the Table \@ref(tab:tab-loads), all models, regardless of the group and order of items, obtained an adequate fit, with CFI's above 0.95 and RMSEA's below 0.08. However, no model achieved a non-significant chi-square (something to be expected in large samples), although both the randomized and the first model obtained an adequate chi-square ratio of less than 3. The first order was the one that obtained the best fit (CFI=0.998, TLI=0.995, RMSEA=0.037, $\chi2$(df=14)=28.03, p = 0.014), followed by the random order of items (CFI=0.992, TLI=0.984,RMSEA=0.051, $\chi2$(df=14)=39.09, p < 0.001). On the other hand, the scale ordered by themes seems to generate a framing effect, in which the relationship between perceptions and preferences seemed to be overestimated, thus affecting the adjustment (CFI=0.984, TLI=0.968, RMSEA=.071, $\chi2$(df=14)=64.156, p < 0.001).

@@

|           | Contrast Model 1 Factor | theoretical model 4 Factors | Model with M.I. |
|:---------:|:-----------------------:|:---------------------------:|:---------------:|
| **n**     |           1769          |             1769            |       1769      |
| **CFI**   |          0.595          |            0.988            |      0.994      |
| **TLI**   |          0.433          |            0.976            |      0.985      |
| **RMSEA** |          0.226          |            0.047            |      0.036      |
| **$\chi2$**    |         1830.839        |            68.661           |      40.250     |
| **p**     |           .000          |             .000            |       .000      |
| **$\chi2$/df** |          65.38          |             4.90            |       3.32      |
Table: `r as.character(paste("(\\#tab:items-dim)", "Items according to dimension."))`.

As shown in Table \@ref(tab:items-dim), the proposed theoretical four-factor model fits better than the one-factor contrast model. The theoretical model adjusted relatively well, as it shows preferable indicators of IFC=0.987, TLI=0.975 and RMSEA=0.041, although it also has poor indicators of $\chi2$(df=14)=67.6 and p-value<0.001. To evaluate possible improvements in the scale, the relationships proposed by the modification indexes were analyzed. These indicate the existence of two unspecified cross-loads. When a model was generated following these recommendations, there was a considerable improvement in the model, although the new model still did not obtain a $\chi2$ ratio of less than 3, and had very low factorial loads ($\tau$)< 0.15. Therefore, following the recommendation of Brown (2006) to only accept the proposals of modification when theory and solid evidence are available, we decided not to incorporate these parameters into the model.

@@

### Longitudinal measurement invariance

@@

_Data_

@@

_Intruments_

@@

- Personal wherewithal: the questionnaire included The Neoliberal Beliefs Inventory (NBI), which consider four factors: [completar] (Bay-Cheng et al., 2015). We used the factor personal wherewithal that reflects meritocracy beliefs in terms of the importance of personal attributes as strength and skills to yield success. The construct consists of 8 items (e.g., “Any goal can be achieved with enough hard work and talent”, “I’ve benefited from working hard, so there’s no reason others can’t”, “Anyone who is willing to work hard can be succesful in Chile”). Participants answered the items using a 1 (totally disagree) to 6 (totally agree) scale. We simple computed mean scores [reportar alfa the cronbach], with higher scores indicating stronger support for meritocracy (M=3.32, SD=0.89, =0.89).

@@

_Results_

@@

We identified four critical aspects regarding the measurement of meritocracy in previous studies: unidimensionality, the ambiguous use of the term “beliefs”, the use of non-meritocratic indicators as opposed to meritocratic indicators, and the consideration of measurement error. The proposed 8-item scale, “Perceptions and Preferences for Meritocracy”, was designed and tested in order to deal with these four issues. Our results indicate that perceptions and preferences seem to be two related but different dimensions, often confounded in previous research under the label of "beliefs". Additionally, meritocratic and non-meritocratic dimensions do not appear to constitute poles of the same continuum, as some previous studies have assumed.

@@

<div id="refs"> </div>  <!-- Although <div> is an HTML tag, this method also works for other output formats such as PDF. -->

# (APPENDIX) Appendix {-}

@@

@@

|                     | Sample  |   CEP  |
|---------------------|:-------:|:------:|
| __Gender__          |         |        |
| Men                 | 49,82%  | 50,52% |
| Women               | 50.18%  | 49,47% |
| __Age__             |         |        |
| 18 - 24             | 18,55%  | 18,17% |
| 25 - 34             | 18,86%  | 17,48% |
| 35 - 44             | 19.09%  | 19,98% |
| 45 - 54             | 17,96%  | 19,23% |
| 55 - or more        | 25,54%  | 25.11% |
| __Education__       |         |        |
| Primary  or less    | 2,93%   | 15,88% |
| High school          | 43,23%  | 37,04% |
| Non university      | 32,63%  | 28,93% |
| university or more  | 21,21%  | 18,13% |
Table: `r as.character(paste("(\\#tab:rep-samp)", "Representativeness of the sample"))`.

>>>>

---
title: "Measuring Perceptions and Preferences for Meritocracy"
css: "custom.css"
linestretch: '1.5'
link-citations: yes
author: "Juan Carlos Castillo, Julio Iturra & Francisco Meneses <br><br>"
abstract: "Economic and social inequalities have generated growing concern and crises across contemporary societies. One of the mechanisms proposed by the social sciences to explain the maintenance of inequality is the belief in meritocracy, which would legitimize economic disparities based on differences in effort and talent. Despite its wide use as a concept, empirical research on meritocracy is relatively novel, and as it is based upon multiple approaches and techniques, its interpretation can be difficult and confusing. Adding to these difficulties, is the fact that many such studies have relied upon secondary data to operationalize meritocracy, with significant variation in the use and interpretation of survey items. Based on a review of studies that measure meritocracy, this article identifies a series of drawbacks and inconsistencies within and between studies regarding the conceptualization and indicators of meritocracy. Based on this critical analysis, we propose a scale named the *Perceptions and Preferences for Meritocracy Scale*, which we test with confirmatory factor analysis, using data from an online survey study (N=2,141). Our results support the proposed conceptual structure, which not only distinguishes between perceptions and preferences, but also between meritocratic and non-meritocratic dimensions. Our discussion highlights the importance of considering these different dimensions in order to advance the study of meritocracy."
output:
  bookdown::pdf_document2:
    template: null
    toc: false
  bookdown::html_document2:
    number_sections: false
linkcolor: blue
bibliography:
  - ../input/bib/EconomiaMoral.bib
  - ../input/bib/meritocracy.bib
  - ../input/bib/invariance.bib
editor_options:
  chunk_output_type: console
  markdown:
    wrap: 72
geometry: margin=0.78in
header-includes:
  # - \usepackage[spanish,es-tabla,es-nodecimaldot]{babel}
  - \usepackage{times}           # Times New Roman
  - \usepackage{caption}
  - \captionsetup[figure, table]{labelfont={bf},labelformat={default},labelsep=period}
  - \usepackage{graphicx}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
---

@@

## The black-box of meritocratic beliefs {#blackbox .unnumbered}

Several approaches to the empirical study of meritocracy based on public
opinion surveys, refer to the concept of *beliefs*, however different
meanings and operationalizations usually underlie this concept. To
illustrate this point, we will take as a main reference a recent paper
about meritocracy by @mijs_paradox_2019, which makes several assumptions
relating to the measurement of meritocracy that are also found in
previous studies. The definition of meritocratic beliefs stated by Mijs
is the following: "when I discuss meritocracy beliefs, I am referring to
citizens' belief in the importance of hard work relative to structural
factors." [@mijs_paradox_2019, pg.9]. In the subsequent
operationalization, this is associated with the following question and
indicator: "how important you think it is for getting ahead in life: (a)
hard work", scored from 1 to 5 on a likert scale. There assumptions
behind this definition are worth discussing in light of the conceptual
meaning of meritocracy and its possibilities of operationalization.

a.  *Unidimensionality*; Is merit only effort?

The item used by @mijs_paradox_2019 is part of an items' battery present
in several international surveys, usually called "reasons to get ahead".
This battery displays a series of indicators related to what people
consider important to get ahead in life: hard work, education, ambition,
a wealthy family, the right connections, religion, race, and gender.
Therefore for Mijs, other aspects that could be associated with talent,
such as education, are not meritocratic. As he points out: "Hard work is
arguably the most meritocratic part of Michael Young's equation: 'Merit
= Intelligence + Effort', for the simple fact that intelligence itself
is influenced by a non-meritocratic factor: who your parents happen to
be" (p.5).

@@

*b. Beliefs*

The most commonly used survey items for the operationalization of
meritocracy is the "reasons to get ahead" battery, which asks "how
important you think it is" and then lists several factors, such as
effort, education, parental wealth, and contacts. Another version of
this same battery used in several surveys - sometimes along the previous
one - asks about "how important you think it *should* be". Therefore,
the question raised here is: Which one of both is a "belief"? What *is*
or what *should* be?

The term belief has an ambiguous character in the literature, conceived
as "idea-elements" by @converseNatureBeliefSystems1964 or
"considerations" by @zallerNatureOriginsMass1992. As
@kluegelBeliefsInequalityAmericans2017 pointed out about the scope of
beliefs: "This usage encompasses such more specific social-psychological
concepts as values, perceptions, and attitudes" (p.30). Therefore,
beliefs cover almost anything related to subjective factors. To this
regard, a relevant distinction in the field of inequality beliefs was
made by @janmaatSubjectiveInequalityReview2013: "Perceptions refer to
subjective estimates of existing inequality (i.e. thoughts about what
is). Beliefs are here defined as normative ideas about just inequality
(i.e. thoughts about what should be)"(p.359). Several papers dealing
with meritocracy use the term beliefs (i.e. what should be), while
actually referring to perceptions (i.e. what is). This occurs not only
in mijs_paradox_2019, but also in @reynolds_perceptions_2014, in which
the term beliefs is used to talk about perceptions, whereas other
authors use general terms such as attitudes (@kunovich_systems_2007).
The first attempt to shed light on this issue was made by
@duru-bellat_whos_2012, who used the question "how important should the
number of years spent in education and training be in deciding how much
money people ought to earn?" as a proxy for "desired" meritocracy
(beliefs). They then determined "perceived" meritocracy, using the
questions: "Would you say that in your country, people are rewarded for
their efforts?" and "... people are rewarded for their skills?".

@@

*c. Non-meritocratic aspects*

Unlike studies that consider talent to be a non-meritocratic aspect, and
therefore rule it out of the operationalization of meritocracy,
@kunovich_systems_2007 follow a different approach, by including some
non-meritocratic elements. Using an items' battery listing a number of
factors in relation to "How important each should be in deciding pay..."
(as @duru-bellat_whos_2012 for desired meritocracy), they consider
factors such as education and responsibility as meritocratic, giving
them a value of 1 if considered "essential" in the scale response,
whereas factors such as having a family or children are valued 1 when
rated as "not important at all" (i.e. reverse coded). The assumption
behind this approach is that rejecting a supposed non-meritocratic
aspect (as having family and/or children) implies a larger belief in
meritocracy. A similar approach of reverse-coding non-meritocratic items
was taken by @newman_false_2015, using the same principles applied in
the "Preference for the Merit Principle Scale" [@davey_preference_1999].

@@

*d. Accounting for measurement error*

@@

## An instrument proposal {#instrumentprop .unnumbered}

@@

-   *Multidimensionality*, incorporating previous distinctions between
    preferences and perceptions, as well as between meritocratic and
    non-meritocratic aspects.

-   Multiple indicators for each dimension, in order to *account for
    measurement error* in a confirmatory factor analysis context.

-   Based on *previous indicators* as much as possible, for the sake of
    comparability between studies.

-   *Brief*, as to be used in regular public opinion surveys. In this
    respect, it differs from the proposal of "Preference for the Merit
    Principle Scale" [@davey_preference_1999], as they use 15 items for
    just one dimension (aside from the problem of reverse-coding
    non-meritocratic items).

@@

-   $H_1$. The perception of meritocracy is a latent variable based on
    indicators of the importance attributed to talent and effort to get
    ahead in life.

-   $H_2$. The perception of non-meritocracy is a latent variable that
    derives from two indicators related to agreement with the statement
    that people with contacts and rich parents manage to get ahead.

-   $H_3$. Meritocratic preferences are a latent variable based on the
    normative value of effort and talent.

-   $H_4$. Non-meritocratic preferences are a latent variable based on
    the normative value of the use of personal contacts and having
    wealthy parents.

@@

## Data collection {#data .unnumbered}

@@

With the objective of evaluating the effect of indicator ordering, the
respondents (*n = 2141*) were randomly divided into three different
set-order versions, as explained in Figure \@ref(fig:appmod). The scale
was presented to the first group (*n = 712*) in the order that appears
in Table 2. For the second group (*n = 717*), the order of the items was
reorganized according to the topics of the items, e.g. for the topic of
hard work, the item about perception was followed by the item about
preference, and the same for the rest of the topics. Finally, for the
third group (*n = 712*), the items were completely randomized.

@@

CFA was conducted using the `lavaan` R package (version 0.6-3; Rosseel,
2020), with diagonally weighted least squares (DWLS) estimation due to
the items' ordinal level of measurement (Kline, 2016; Rosseel, 2020). As
recommended by Brown (2008), we assessed model fit by jointly
considering the comparative fit index and Tucker-Lewis Index (CFI and
TLI; acceptable fit \> 0.95), Root of the average squared residual
approximation (RMSEA; acceptable fit \< 0.08), Chi-square: (p-value;
acceptable fit \> 0.05, and Chi-square ratio \> 3).

A pre-registration was made in the OSF platform, available at the
following link: <https://osf.io/z45y2>. Included in this
pre-registration are the hypotheses regarding the four-dimensional
conceptual model underlying the scale, the variable measurement levels,
the statistical tests to be performed with their respective evaluation
parameters, and other important aspects of the research design.

@@

As can be seen in the Table \@ref(tab:tab-loads), all models, regardless
of the group and order of items, obtained an adequate fit, with CFI's
above 0.95 and RMSEA's below 0.08. However, no model achieved a
non-significant chi-square (something to be expected in large samples),
although both the randomized and the first model obtained an adequate
chi-square ratio of less than 3. The first order was the one that
obtained the best fit (CFI=0.998, TLI=0.995, RMSEA=0.037,
$\chi2$(df=14)=28.03, p = 0.014), followed by the random order of items
(CFI=0.992, TLI=0.984,RMSEA=0.051, $\chi2$(df=14)=39.09, p \< 0.001). On
the other hand, the scale ordered by themes seems to generate a framing
effect, in which the relationship between perceptions and preferences
seemed to be overestimated, thus affecting the adjustment (CFI=0.984,
TLI=0.968, RMSEA=.071, $\chi2$(df=14)=64.156, p \< 0.001).

@@

|            | Contrast Model 1 Factor | theoretical model 4 Factors | Model with M.I. |
|:----------:|:-----------------------:|:---------------------------:|:---------------:|
|   **n**    |          1769           |            1769             |      1769       |
|  **CFI**   |          0.595          |            0.988            |      0.994      |
|  **TLI**   |          0.433          |            0.976            |      0.985      |
| **RMSEA**  |          0.226          |            0.047            |      0.036      |
|  $\chi2$   |        1830.839         |           68.661            |     40.250      |
|   **p**    |          .000           |            .000             |      .000       |
| $\chi2$/df |          65.38          |            4.90             |      3.32       |

: `r as.character(paste("(\\#tab:items-dim)", "Items according to dimension."))`.

As shown in Table \@ref(tab:items-dim), the proposed theoretical
four-factor model fits better than the one-factor contrast model. The
theoretical model adjusted relatively well, as it shows preferable
indicators of IFC=0.987, TLI=0.975 and RMSEA=0.041, although it also has
poor indicators of $\chi2$(df=14)=67.6 and p-value\<0.001. To evaluate
possible improvements in the scale, the relationships proposed by the
modification indexes were analyzed. These indicate the existence of two
unspecified cross-loads. When a model was generated following these
recommendations, there was a considerable improvement in the model,
although the new model still did not obtain a $\chi2$ ratio of less than
3, and had very low factorial loads ($\tau$)\< 0.15. Therefore,
following the recommendation of Brown (2006) to only accept the
proposals of modification when theory and solid evidence are available,
we decided not to incorporate these parameters into the model.

@@

### Measurement invariance

*Datos*

Para el desarrollo de esta sección, se empleó una fuente de datos
externa a los resultados presentados en el apartado anterior. Los datos
provienen de un estudio realizado durante el primer semestre de 2020,
dentro del cual se realizó una medición usando la escala a través de
aleatorización completa de los indicadores, lo cual corresponde a la
modalidad de aplicación del Grupo 3 presente en la Figura
\@ref(fig:appmod). Después de la eliminación de casos perdidos por
lista, obtuvimos una muestra analítica final de 1242 casos donde 605
(48,71%) son mujeres y 637 (51,28%) son hombres. El 48,84% de ellos
tienen 45 años o más, y el 33,97% poseen educación terciaria o superior.
En la Tabla \@ref(tab:factloads2) se pueden observar los resultados del ajuste de la
escala en esta muestra. Análisis El modelamiento para el testeo
invarianza consiste en una serie de modelos anidados a los que
progresivamente se le van incorporando restricciones sobre los
parámetros del modelo de medición , permitiendo esta progresión
localizar la fuente de una violación de invarianza, lo cual ha sido
tomando mayor relevancia en los estudios sociológicos a través de
encuestas, principalmente por la validez del uso de escalas de medición
en estudios de carácter comparado en diversos contextos sociales y
culturales [@Davidovetal2014]. En esta sección emplearemos un análisis
de invarianza entre grupos, donde se espera que la estructura factorial
sea independiente de la pertenencia a las la muestra correspondiente al
estudio original y a los datos del estudio más reciente. Para el
desarrollo del test de invarianza, los autores sostienen que el
modelamiento debe realizarse a través de cuatro niveles o tipos de
restricción progresiva [@Milfont2010; @millsap_Statistical_2011;
@vandeschoot_checklist_2012]:

1.  **Configural:** Se estima el Modelo solo de indicando la estructura
    de este, razón por lo cual todos los parámetros se estiman
    libremente.

2.  **Débil:** Posteriormente, en el modelo se restringen las cargas
    factoriales de cada ítem, haciéndolas idénticas en ambas mediciones.

3.  **Fuerte:** Luego, se estima el modelo restringiendo las cargas
    factoriales y los interceptos de cada ítem, haciéndolos idénticos
    para cada ambas mediciones.

4.  **Estricta:** Finalmente, se estima un modelo donde se restringen
    las cargas factoriales, los interceptos y las varianzas de error
    para cada ítem, haciéndolos idénticos para ambas mediciones.

El primer paso para el testeo de invarianza es la estimación del modelo
Configural, el cual se espera que cumpla adecuadamente con los criterios
de ajuste global de un modelo de medición, debido a que es el modelo
base en proceso de comparación. Convencionalmente el estadístico
chi-cuadrado es empleado como medida global de ajuste de un modelo de
medición. Sin embargo, al ser sensible al tamaño de la muestra, se
recomienda emplear tres índices de ajuste adicionales: Comparative Fit
Index (CFI), el cual debe tener un valor mayor a 0.9; Root Mean Square
Error Approximation (RMSEA), el cual debe estar en el rango de valores
de 0.05 y 0.08; y el Standardised Root Mean Square Residuals (SRMR) que
debe ser menor a 0.08 (@vandeschoot_checklist_2012)

La literatura sobre invarianza métrica sugiere dos aproximaciones
complementarias para el testeo de invarianza. En nuestro caso,
emplearemos la comparación basada en el ajuste incremental de los
estadísticos de ajuste [@cheung_Evaluating_2002; @Milfont2010;
@dimitrov_Testing_2010] y el test ANOVA para comparación de medias en
modelos anidados [@newsom_Longitudinal_2015].

```{r invargroup, eval=TRUE, echo=FALSE}
load(file = "../output/tables/tb.inv-group.RData")
col.nam <- c("Model","$\\chi^2 (\\text{df})$","CFI","RMSEA (90 CI)",
             "$\\Delta \\chi^2 (\\Delta \\text{df}$)","$\\Delta \\text{CFI}$","$\\Delta \\text{RMSEA}$","Decision")
footnote <- paste0("N = ",nobs(conf),"; Group 1, n = ",conf@Data@nobs[[1]],"; Group 2, n = ",conf@Data@nobs[[2]], "***p < .001")

kable(tab.inv, col.names = col.nam, align = "l",
      booktabs=TRUE,format = table_format,escape = FALSE,
      caption = "Multiple Group meassurement invariance Perceptions and Preferences for Meritocracy") %>% 
  kable_styling(full_width = FALSE) %>%
  footnote(general = footnote, footnote_as_chunk = T)
```

Como se puede observar en la Table \@ref(tab:invargroup)

@@

*Data*

@@

*Intruments*

@@

-   Personal wherewithal: the questionnaire included The Neoliberal
    Beliefs Inventory (NBI), which consider four factors: [completar]
    (Bay-Cheng et al., 2015). We used the factor personal wherewithal
    that reflects meritocracy beliefs in terms of the importance of
    personal attributes as strength and skills to yield success. The
    construct consists of 8 items (e.g., "Any goal can be achieved with
    enough hard work and talent", "I've benefited from working hard, so
    there's no reason others can't", "Anyone who is willing to work hard
    can be succesful in Chile"). Participants answered the items using a
    1 (totally disagree) to 6 (totally agree) scale. We simple computed
    mean scores [reportar alfa the cronbach], with higher scores
    indicating stronger support for meritocracy (M=3.32, SD=0.89,
    =0.89).

@@

*Results*

@@

We identified four critical aspects regarding the measurement of
meritocracy in previous studies: unidimensionality, the ambiguous use of
the term "beliefs", the use of non-meritocratic indicators as opposed to
meritocratic indicators, and the consideration of measurement error. The
proposed 8-item scale, "Perceptions and Preferences for Meritocracy",
was designed and tested in order to deal with these four issues. Our
results indicate that perceptions and preferences seem to be two related
but different dimensions, often confounded in previous research under
the label of "beliefs". Additionally, meritocratic and non-meritocratic
dimensions do not appear to constitute poles of the same continuum, as
some previous studies have assumed.

@@

::: {#refs}
:::

<!-- Although <div> is an HTML tag, this method also works for other output formats such as PDF. -->

# (APPENDIX) Appendix {.unnumbered}

@@

```{r factloads2}
load(file = "../output/tables/tb.fact-f02.RData")
tb.fm01<- kable(tb.fm,escape = FALSE,align = "lcccc",col.names = tb.col, caption = tb.caption) %>% 
          kable_styling(full_width = F,font_size = 9) %>% 
          add_header_above(header = c(" "=1,"Factor loadings"= 4)) %>%
          column_spec(column = 1,width = "5cm") %>% 
          column_spec(column = c(2:5),width = "0.5cm") %>% 
          row_spec(row = 8,hline_after = TRUE) %>%
          add_indent(c(9:12)) %>% 
          footnote(general =tb.foot ,footnote_as_chunk = T);tb.fm01
```

@@

|                    | Sample |  CEP   |
|--------------------|:------:|:------:|
| **Gender**         |        |        |
| Men                | 49,82% | 50,52% |
| Women              | 50.18% | 49,47% |
| **Age**            |        |        |
| 18 - 24            | 18,55% | 18,17% |
| 25 - 34            | 18,86% | 17,48% |
| 35 - 44            | 19.09% | 19,98% |
| 45 - 54            | 17,96% | 19,23% |
| 55 - or more       | 25,54% | 25.11% |
| **Education**      |        |        |
| Primary or less    | 2,93%  | 15,88% |
| High school        | 43,23% | 37,04% |
| Non university     | 32,63% | 28,93% |
| university or more | 21,21% | 18,13% |

: `r as.character(paste("(\\#tab:rep-samp)", "Representativeness of the sample"))`.

### 2020-12-21 production/prod_analysis-group_invariance.rmd
update sección invarianza

#------ merge ------#
tb.fm<- bind_rows(loads01,fm.df)
tb.fm<- tb.fm %>% 
  mutate(vars=c(labs,"$\\chi^2\\text{(df)}$","$\\text{CFI}$","$\\text{RMSEA}$","$N$")) %>%
  select(vars,everything())
#--table---#
tb.col  <- c("Variables",1:4)
tb.foot <- paste0("; p<0.05=$^{*}$; p<0.01=$^{**}$; p<0.001=$^{***}$. Standardised factor loadings using DWLS estimator. CFI = Comparative fit index (scaled), RMSEA = Root mean square error of approximation (scaled)")
tb.caption <- "Factor loadings and fit measures"

@@

save(tb.fm,file = "output/tables/tb.fact-f02.RData")
```

@@

save(tab.inv,file = "output/tables/tb.inv-group.RData")
```

>>>>

#------ merge ------#
tb.fm<- bind_rows(loads01,fm.df)
tb.fm<- tb.fm %>% 
  mutate(vars=c(labs,"$\\chi^2\\text{(df)}$","$\\text{CFI}$","$\\text{RMSEA}$","$N$")) %>%
  select(vars,everything())
#--table---#
tb.col  <- c("Variables",1:4)
tb.foot <- paste0("; p<0.05=$^{*}$; p<0.01=$^{**}$; p<0.001=$^{***}$. Standardised factor loadings using DWLS estimator. CFI = Comparative fit index (scaled), RMSEA = Root mean square error of approximation (scaled)")
tb.caption <- "Factor loadings and fit measuresfor the second sample"

@@

save(tb.fm,tb.col,tb.foot,tb.caption,file = "output/tables/tb.fact-f02.RData")
```

@@

save(tab.inv,conf,file = "output/tables/tb.inv-group.RData")
```
